Formatting Instructions for CoRL 2022

### 2022-06-02 CORL/example.tex
Added authors
Set to final mode

\usepackage{corl_2022} % Use this for the initial submission.
%\usepackage[final]{corl_2022} % Uncomment for the camera-ready ``final'' version.
%\usepackage[preprint]{corl_2022} % Uncomment for pre-prints (e.g., arxiv); This is like ``final'', but will remove the CORL footnote.

@@

\author{
  Jane E.~Doe\\
  Department of Electrical Engineering and Computer Sciences\\
  University of California Berkeley 
  United States\\
  \texttt{janedoe@berkeley.edu} \\
  %% examples of more authors
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \AND
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
}

>>>>

% \usepackage{corl_2022} % Use this for the initial submission.
\usepackage[final]{corl_2022} % Uncomment for the camera-ready ``final'' version.
%\usepackage[preprint]{corl_2022} % Uncomment for pre-prints (e.g., arxiv); This is like ``final'', but will remove the CORL footnote.

@@

\author{%
	Ryan Burgert \\
	Department of Computer Science\\
	Stony Brook University\\
	Stony Brook, NY 11794 \\
	\texttt{rburgert@cs.stonybrook.edu} \\
	% \And
	% Michael Ryoo \\
	% Department of Computer Science\\
	% Stony Brook University\\
	% Stony Brook, NY 11794 \\
	% \texttt{mryoo@cs.stonybrook.edu} \\
	\And
	Emma Burgert \\
	Ryan Burgert's Dog\\
}
